### 2016-06-08 paper/icfp16-cameraready/introduction.tex
misc

\paragraph{1. Finding Witnesses}
Our first contribution is an algorithm for searching for
\emph{witnesses} to type errors, \ie\ inputs that cause a
program to go wrong~(\S~\ref{sec:semantics}).
%
This problem is surprisingly tricky when we cannot rely on
static type information.
%
In particular, we must avoid the trap of \emph{spurious} inputs
that cause irrelevant problems that would be avoided by picking
values of a different, relevant type.
%
We solve this problem by developing a novel operational semantics
that combines evaluation and type inference.
%
We execute the program with \emph{holes} --- values whose type is
unknown --- as the inputs.
% that corresponds to executing the program with \emph{holes} ---
% values whose type is unknown.
%
A hole remains abstract until the evaluation context tells us what type
it must have, for example the parameters to an addition operation must
both be integers.
%
Our semantics \emph{conservatively} instantiates holes with concrete
values; thereby dynamically inferring the type of the input
until the program goes wrong.
%
We prove that our procedure synthesizes \emph{general witnesses}, which
means, intuitively, that if a witness is found for a given ill-typed
function, then, \emph{for all} (inhabited) input types, there exist
values that can make the function go wrong.

@@

\paragraph{3. Evaluating Witnesses}
%
Of course, the problem of finding witnesses is
undecidable. In fact, due to the necessarily
conservative nature of static typing, there
may not even exist any witnesses for a given
ill-typed program.
%
Thus, our approach is a heuristic that is only useful
if it can find \emph{compact} witnesses for
\emph{real-world} programs.
%
Our third contribution is an extensive evaluation of our approach
on two different sets of ill-typed programs obtained by instrumenting
compilers used in beginner's classes~(\S~\ref{sec:evaluation}).
%
The first is the \uwbench\ data set~\cite{Lerner2007-dt}
comprising \uwsize\ ill-typed programs.
%
The second is a new \ucsdbench\ data set, comprising \ucsdsize\
ill-typed programs.
%
We show that for both data sets, our technique is able to generate
witnesses for nearly 90\% of the programs, in under a second in the
vast majority of cases.
%
Furthermore, we show that a simple interactive strategy yields
compact counterexample traces with at most 5 steps for 57\%
of the programs, and at most 10 steps for 81\% of the programs.

>>>>

\paragraph{1. Finding Witnesses}
Our first contribution is an algorithm for searching for
\emph{witnesses} to type errors, \ie\ inputs that cause a
program to go wrong~(\S~\ref{sec:searching-witness}).
%
This problem is surprisingly tricky when we cannot rely on
static type information.
%
In particular, we must avoid the trap of \emph{spurious} inputs
that cause irrelevant problems that would be avoided by picking
values of a different, relevant type.
%
We solve this problem by developing a novel operational semantics
that combines evaluation and type inference.
%
We execute the program with \emph{holes} --- values whose type is
unknown --- as the inputs.
% that corresponds to executing the program with \emph{holes} ---
% values whose type is unknown.
%
A hole remains abstract until the evaluation context tells us what type
it must have, for example the parameters to an addition operation must
both be integers.
%
Our semantics \emph{conservatively} instantiates holes with concrete
values; thereby dynamically inferring the type of the input
until the program goes wrong.
%
We prove that our procedure synthesizes \emph{general witnesses}, which
means, intuitively, that if a witness is found for a given ill-typed
function, then, \emph{for all} (inhabited) input types, there exist
values that can make the function go wrong.

@@

\paragraph{3. Evaluating Witnesses}
%
Of course, the problem of finding witnesses is
undecidable in general. In fact, due to the necessarily
conservative nature of static typing, there
may not even exist any witnesses for a given
ill-typed program.
%
Thus, our approach is a heuristic that is only useful
if it can find \emph{compact} witnesses for
\emph{real-world} programs.
%
Our third contribution is an extensive evaluation of our approach
on two different sets of ill-typed programs obtained by instrumenting
compilers used in beginner's classes~(\S~\ref{sec:evaluation}).
%
The first is the \uwbench\ data set~\cite{Lerner2007-dt}
comprising \uwsize\ ill-typed programs.
%
The second is a new \ucsdbench\ data set, comprising \ucsdsize\
ill-typed programs.
%
We show that for both data sets, our technique is able to generate
witnesses for nearly 90\% of the programs, in under a second in the
vast majority of cases.
%
Furthermore, we show that a simple interactive strategy yields
compact counterexample traces with at most 5 steps for 57\%
of the programs, and at most 10 steps for 81\% of the programs.
